Concurrent and Distributed Programming in Harmony

### 2022-01-13 paper/paper.tex
Latest

>>>>

\section{Harmony Compiler}

The compiler translates the Harmony language to a sequence of HVM
instructions.  The compiler is mostly straightforward.  This section
describes some of its unusual features.

To help the programmer reason about the behavior of the generated code,
the compiler preserves the left-to-right evaluation order of
expresssions.  In other words, if expression $e_1$ appears before
$e_2$ in the source language, then $e_1$ is evaluated before $e_2$
in the HVM translation.  There is one exception, for the Harmony/Python
$e_1~<{if}>~c~<{else}>~e_2$ expression, $c$ is evaluated first, and
depending on the outcome, either $e_1$ or $e_2$ is evaluated.

The compiler performs some standard optimizations that do not re-order
expression evaluations, such as constant folding and jump threading.
A more interesting optimization is \emph{dead variable elimination}:
local variables that are no longer in use are automatically removed
from the state using the HVM \texttt{DelVar} instruction.  The reason
for this is to reduce state explosion by removing state that is no
longer in use.
